Modulation and delays in Fourier domain: precessing binaries and LISA-type detector response

### 2016-07-02 docs/paper_method.tex
Small changes to datura Makefile and to the paper.

To obtain~\eqref{eq:resultdffPsi}, we expanded the exponential. If we keep it as it is, however, we have
%
\begin{subequations}
\begin{align}
	\tilde{s}(f) &= \tilde{h}(f) \int\ud f'\, \tilde{F}(f') e^{-2i\pi f'\tf} \exp\left[ -\frac{i}{2} \frac{\ud^{2} \Psi}{\ud f^{2}} {f'}^{2} \right] \, \\
	&= \tilde{h}(f) \int \ud t\, F(t) \int\ud f'\, e^{2i\pi f' (t-\tf)} \exp\left[ 2i\pi^{2} \epsilon{f'}^{2} \Tf^{2} \right] \,,
\end{align}
\end{subequations}
%
where we recall that $\epsilon = -\mathrm{sgn}(\ud ^{2} \Psi/\ud f^{2})$. The resulting Gaussian integral yields [check how $\epsilon$ propagates]
%
\begin{subequations}
\begin{align}\label{eq:resultFresnel}
	\tilde{s}(f) &= \tilde{h}(f) \calF_{\Tf}[F](\tf)^{*} \quad \text{if } \epsilon = 1 \,,\\
	\tilde{s}(f) &= \tilde{h}(f) \calF_{\Tf}[F](\tf) \quad \text{if } \epsilon = -1 \,,
\end{align}
\end{subequations}
%
where we introduced the Fresnel transform~\cite{} of $F$, defined as follows:
%
\be\label{eq:defFresnel}
	\calF_{\tau}[F](t_{0}) \equiv \frac{e^{-i\frac{\pi}{4}}}{\sqrt{2\pi} \tau} \int \ud t \, \exp\left[ \frac{i}{2} \left( \frac{t-t_{0}}{\tau} \right)^{2}\right] F(t) \,.
\ee
%
The Fresnel transform applies to a large class of functions [be more precise] and intervenes in the theory of diffraction [give references and examples]. Although it is interesting to be able to relate our results to a known transformation used in signal processing, whether this opens avenues for efficient computation methods remains to be investigated (for instance by performing a linear decomposition of the modulation $F$ in wavelets, or chirplets, which have analytically computable Fresnel transforms).

@@

The authors of~\cite{} did not reformulate their result as in~\eqref{eq:resultFresnel}, but they proposed  a resummation scheme. Indeed, the result~\eqref{} looks like a symmetrixed Taylor expansion, except for the factors $i^{p}$ and $1/p!$ instead of $1/(2p)!$. After having truncated the sum at some finite $N$, one can write
%
\begin{align}\label{eq:resum}
	\tilde{s}(f) &\simeq \tilde{h}(f) \sum\limits_{p = 0}^{N} \frac{(-i\epsilon\Tf^{2})^{p}}{2^{p}p!} \partial_{t}^{2p}F(\tf) \nn\\
	&\simeq \tilde{h}(f) \sum\limits_{p= 0}^{N} \sum\limits_{k=0}^{N} a_{N,k}\frac{(k\Tf)^{2p}}{(2p)!}  \partial_{t}^{2p}F(\tf) \nn\\
	&\simeq \tilde{h}(f) \frac{1}{2}\sum\limits_{k=0}^{N} a_{N,k} \left( F(\tf + k\Tf) + F(t-k\Tf) \right)\,,
\end{align}
%
where we applied a truncation approximation at the first and last stage. The second equality holds provided that the complex coefficients $a_{N,k}$ are a solution of the $N+1$-dimensional linear system
%
\be
	(-i\epsilon)^{p} (2p-1)!! = \sum\limits_{k=0}^{N} a_{N,k} k^{2p} \quad \text{for } p=0,\dots,N \,.
\ee
%
The two solutions for the comb coefficients in the two cases $\epsilon = \pm 1$ are simply related by a complex conjugation.

@@

This seems to good to be true. In general, one could have made any ansatz for the series expansion to be matched on, and one therefore cannot expect in general nice properties to emerge from a resummation. However, the transformation~\eqref{} between the two series above has a special structure. Namely, written in matrix form, the linear system is a Vandermonde system. Defining the Vandermonde matrix $V(x_{0},\dots,x_{N})$ as $V_{ij} = (x_{j})^{i}$ (with the convention $0^{0} = 1$), setting $x_{j} = j^{2}$, the linear system is simply
%
\be
	b_{p} = V_{p,k} a_{N,k} \,.
\ee
%
Now, since the Vandermonde system solves the Lagrange polynomial interpolation problem, we know that . Namely, $({}^{t}V^{-1})_{ij}$ is the coefficient of $X^{i}$ in the polynomial $\prod_{k\neq j} (X-x_{k})/(x_{j} - x_{k})$. If we introduce the symmetric polynomials $\sigma$ such that
%
\be	
	\sigma(m, \{x_{1}, \dots, x_{n}\}) = \sum\limits_{1\leq i_{1}<\dots<i_{m}\leq n} x_{i_{1}}\dots x_{i_{m}} \,,
\ee
%
we obtain for the inverse of the matrix $V$
%
\be
	V^{-1}_{ij} = \frac{1}{\prod_{k\neq i} (i^{2} - k^{2})} (-1)^{N-j} \sigma(N-j, \{0,\dots,N^{2}\}\backslash \{i^{2}\}) \,.
\ee
%
This allows us to write an ``analytical'' expression for the $a_{N,k}$ for every finite order $N$:
%
\be
	a_{N,k} = \sum\limits_{p=0}^{N} (-i\epsilon)^{p}(2p-1)!! \frac{(-1)^{N-p}}{\prod_{k\neq p} (p^{2}-k^{2})} \sum\limits_{\substack{ 0 \leq i_{1} < \dots < i_{N-p} \leq N \\ i_{1}, \dots, i_{N-p} \neq p}} i_{1}^{2}\dots i_{N-p}^{2}
\ee
%
The combinatorial explosion of the number of terms in the symmetric polynomials, however, makes this expression impractical to evaluate for $N$ beyond a few dozen. It could allow, however, one to control the asymptotics and maybe prove the convergence or non-convergence of the sequence of $a_{N,k}$ for $N\rightarrow +\infty$. [wishful thinking]

>>>>

To obtain~\eqref{eq:resultdffPsi}, we expanded the exponential. If we keep it as it is, however, we have
%
\begin{subequations}
\begin{align}
	\tilde{s}(f) &= \tilde{h}(f) \int\ud f'\, \tilde{F}(f') e^{-2i\pi f'\tf} \exp\left[ -\frac{i}{2} \frac{\ud^{2} \Psi}{\ud f^{2}} {f'}^{2} \right] \, \\
	&= \tilde{h}(f) \int \ud t\, F(t) \int\ud f'\, e^{2i\pi f' (t-\tf)} \exp\left[ 2i\pi^{2} \epsilon{f'}^{2} \Tf^{2} \right] \,,
\end{align}
\end{subequations}
%
where we recall that $\epsilon = -\mathrm{sgn}(\ud ^{2} \Psi/\ud f^{2})$. The resulting Gaussian integral yields [check how $\epsilon$ propagates]
%
\begin{subequations}
\begin{align}\label{eq:resultFresnel}
	\tilde{s}(f) &= \tilde{h}(f) \calF_{\Tf}[F](\tf) \quad \text{if } \epsilon = 1 \,,\\
	\tilde{s}(f) &= \tilde{h}(f) \calF_{\Tf}[F](\tf)^{*} \quad \text{if } \epsilon = -1 \,,
\end{align}
\end{subequations}
%
where we introduced the Fresnel transform~\cite{} of $F$, defined as follows:
%
\be\label{eq:defFresnel}
	\calF_{\tau}[F](t_{0}) \equiv \frac{e^{i\frac{\pi}{4}}}{\sqrt{2\pi} \tau} \int \ud t \, \exp\left[ - \frac{i}{2} \left( \frac{t-t_{0}}{\tau} \right)^{2}\right] F(t) \,.
\ee
%
The Fresnel transform applies to a large class of functions [be more precise] and intervenes in the theory of diffraction [give references and examples]. Although it is interesting to be able to relate our results to a known transformation used in signal processing, whether this opens avenues for efficient computation methods remains to be investigated (for instance by performing a linear decomposition of the modulation $F$ in wavelets, or chirplets, which have analytically computable Fresnel transforms).

@@

The authors of~\cite{} did not reformulate their result as in~\eqref{eq:resultFresnel}, but they proposed  a resummation scheme. Indeed, the result~\eqref{} looks like a symmetrixed Taylor expansion, except for the factors $i^{p}$ and $1/p!$ instead of $1/(2p)!$. After having truncated the sum at some finite $N$, one can write
%
\begin{align}\label{eq:resum}
	\tilde{s}(f) &\simeq \tilde{h}(f) \sum\limits_{p = 0}^{N} \frac{(-i\epsilon\Tf^{2})^{p}}{2^{p}p!} \partial_{t}^{2p}F(\tf) \nn\\
	&\simeq \tilde{h}(f) \sum\limits_{p= 0}^{N} \sum\limits_{k=0}^{N} a_{N,k}\frac{(k\Tf)^{2p}}{(2p)!}  \partial_{t}^{2p}F(\tf) \nn\\
	&\simeq \tilde{h}(f) \frac{1}{2}\sum\limits_{k=0}^{N} a_{N,k} \left( F(\tf + k\Tf) + F(\tf-k\Tf) \right)\,,
\end{align}
%
where we applied a truncation approximation at the first and last stage. The second equality holds provided that the complex coefficients $a_{N,k}$ are a solution of the $N+1$-dimensional linear system
%
\be
	(-i\epsilon)^{p} (2p-1)!! = \sum\limits_{k=0}^{N} a_{N,k} k^{2p} \quad \text{for } p=0,\dots,N \,.
\ee
%
The two solutions for the comb coefficients in the two cases $\epsilon = \pm 1$ are simply related by a complex conjugation.

@@

This seems to good to be true. In general, one could have made any ansatz for the series expansion to be matched on, and one therefore cannot expect in general nice properties to emerge from a resummation. However, the transformation~\eqref{} between the two series above has a special structure. Namely, written in matrix form, the linear system is a Vandermonde system. Defining the Vandermonde matrix $V(x_{0},\dots,x_{N})$ as $V_{ij} = (x_{j})^{i}$ (with the convention $0^{0} = 1$), setting $x_{j} = j^{2}$, and $b_{p} \equiv (-i\epsilon)^{p}(2p-1)!!$, the linear system is simply
%
\be
	b_{p} = V_{p,k} a_{N,k} \,.
\ee
%
Now, since the Vandermonde system solves the Lagrange polynomial interpolation problem, we know that . Namely, $({}^{t}V^{-1})_{ij}$ is the coefficient of $X^{i}$ in the polynomial $\prod_{k\neq j} (X-x_{k})/(x_{j} - x_{k})$. If we introduce the symmetric polynomials $\sigma$ such that
%
\be	
	\sigma(m, \{x_{1}, \dots, x_{n}\}) = \sum\limits_{1\leq i_{1}<\dots<i_{m}\leq n} x_{i_{1}}\dots x_{i_{m}} \,,
\ee
%
we obtain for the inverse of the matrix $V$
%
\be
	V^{-1}_{ij} = \frac{1}{\prod_{k\neq i} (i^{2} - k^{2})} (-1)^{N-j} \sigma(N-j, \{0,\dots,N^{2}\}\backslash \{i^{2}\}) \,.
\ee
%
This allows us to write an ``analytical'' expression for the $a_{N,k}$ for every finite order $N$:
%
\be
	a_{N,k} = \sum\limits_{p=0}^{N} (-i\epsilon)^{p}(2p-1)!! \frac{(-1)^{N-p}}{\prod_{j\neq k} (j^{2}-k^{2})} \sum\limits_{\substack{ 0 \leq i_{1} < \dots < i_{N-p} \leq N \\ i_{1}, \dots, i_{N-p} \neq k}} i_{1}^{2}\dots i_{N-p}^{2}
\ee
%
The combinatorial explosion of the number of terms in the symmetric polynomials, however, makes this expression impractical to evaluate for $N$ beyond a few dozen. It could allow, however, one to control the asymptotics and maybe prove the convergence or non-convergence of the sequence of $a_{N,k}$ for $N\rightarrow +\infty$. [wishful thinking]
